% Common input to both userManual and to devManual.  
% AJR, Feb--Mar 2019
%!TEX root = eqnFreeDevMan.tex


\author{A.~J.~Roberts\thanks{%
School of Mathematical Sciences, University of Adelaide, South Australia.
\url{http://www.maths.adelaide.edu.au/anthony.roberts},
\url{http://orcid.org/0000-0001-8930-1552}}
\and John~Maclean\thanks{%
School of Mathematical Sciences, University of Adelaide, South Australia.
\url{http://www.adelaide.edu.au/directory/john.maclean}}
\and J.~E.~Bunder\thanks{%
School of Mathematical Sciences, University of Adelaide, South Australia.
\protect\url{mailto:judith.bunder@adelaide.edu.au},
\protect\url{http://orcid.org/0000-0001-5355-2288}}
\and et~al.\thanks{Appear here for your contribution.}
}

\date{\today}

% For some reason, refart needs this??
\renewcommand{\and}{\hspace{2em plus 1em minus 1em}}


%% I guess we should abandon these alternatives
%\IfFileExists{ajr.sty}{\usepackage{ajr}}{
%  \IfFileExists{jm.sty}{\usepackage{jm}}{
%    \usepackage[a5paper,margin=11mm]{geometry}
%}}  

\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{xcolor}


\usepackage{pgfplots} 
\pgfplotsset{compat=newest} % AJR: changed to newest aiming for flexible
\usepgfplotslibrary{external} %exports an external pdf for each tikz figure
%\tikzexternalize
%% To force redraw of all tikz graphics (or rm *.md5):
%\tikzset{external/force remake}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{shapes,arrows,fit}
\usetikzlibrary{positioning}

% What do we need these for??
%\usepackage{bold-extra}
%\usepackage{caption}
\def\figurename{\em Figure}

% fancyvrb does code listing, including line numbers
\usepackage{fancyvrb}
\newenvironment{matlab}%
    {\Verbatim[numbers=left,firstnumber=\the\inputlineno]}%
    {\endVerbatim}
% Also get fancyvrb to omit %{ and %} pairs, 
% although this requires they always be used
\makeatletter
\def\fancyvrbStartStop{%
  \edef\FancyVerbStartString{\@percentchar\@charrb} 
  \edef\FancyVerbStopString{\@percentchar\@charlb} }
\makeatother
% could change appearance with e.g. \renewcommand{\theFancyVerbLine}{%
%  \textcolor{red}{\small 8.\alph{FancyVerbLine}}}


\usepackage{natbib}
\bibliographystyle{agsm}
\AtBeginDocument{\let\harvardurl\url}

% used to in/exclude
\usepackage{versions}
\newenvironment{devMan}{}{} % material for only the developers manual
\newenvironment{userMan}{}{} %


\usepackage{url,microtype,amsmath,amssymb,defns,graphicx,hyperref,doi}
\hypersetup{colorlinks,linkcolor=RoyalBlue,citecolor=RoyalBlue,pagecolor=RoyalBlue,%
            urlcolor=magenta,filecolor=magenta,breaklinks,%
            dvips,bookmarks,bookmarksopen}
\makeatletter
\AtBeginDocument{{\def\and{, }\def\thanks#1{}%
  \hypersetup{
    pdfauthor={\@author},
    pdftitle={\@title}}}
    }
\makeatother
% Invoke cleverref
\usepackage[capitalise,nameinlink,noabbrev]{cleveref}
\crefname{equation}{}{}
% Default "Item" useless, use enumitem and ref=
\crefname{enumi}{}{}
\crefname{enumii}{}{}
\crefname{enumiii}{}{}
\crefname{enumiv}{}{}

% command definitions
\def\into{\(\leftrightarrow\)\ }
\Vec f\Vec x\Vec u \Vec X \Vec U
\Bb R  \Bb X


\usepackage[onedeep]{etocx}% for mini-local-tableofconents, best loaded last??


\graphicspath{{../ProjInt/Figs/}{../Patch/Figs/}}



\begin{document}
\epstopdfsetup{suffix=} % must be after begin{document}

\maketitle

\begin{abstract}
This `equation-free toolbox' empowers the computer-assisted analysis of complex, multiscale systems.
Its aim is to enable you to use microscopic simulators to perform system level tasks and analysis.
The methodology bypasses the derivation of macroscopic evolution equations by using only short bursts of microscale simulations which are often the best available description of a system
\cite[e.g.]{Kevrekidis09a, Kevrekidis04a, Kevrekidis03b}.
This suite of functions should empower users to start implementing such methods---but so far we have only just started.
\end{abstract}

\tableofcontents

\ifUserNotDev \excludeversion{devMan}
\else         \excludeversion{userMan}
\fi

\include{introduction}

\fancyvrbStartStop 


\include{projInt}

\include{patch}


% only include appendices in the devManual
\begin{devMan}
%
\appendix
\let\FancyVerbStartString\relax 
\let\FancyVerbStopString\relax
\include{appContribute}
\include{apptpd}
%
\end{devMan}


% get bib data from shared and local files; 
% add required local to shared with 'bibexport equationFreeDoc'
\IfFileExists{ajr.sty}{\bibliography{bibexport,ajr,bib}}{}
\IfFileExists{jm.sty}{\bibliography{bibexport,jm,bib}}{}

\end{document}
